\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-12-08 AffineLieAlgebras/InformalNotes/article.tex
Some work with the placement of the pictures.

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=120mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$.\\ Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, \\dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
  \label{fig:a1a2a3}
\end{figure}

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.
\begin{comment}
  It seems that here $\Gamma$ should include only two points. Is it true?

  Think of the pictures more.
\end{comment}
Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
\begin{equation}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
\end{equation}
So we have computed the branching coefficients.
\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
We calculate the branching coefficients for the fundamental representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$
\begin{figure}[h]
  \includegraphics[width=150mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

\begin{comment}
  Change ``enveloping'' into something better.
\end{comment}
Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for enveloping and embedded theory.

>>>>

In the case of special embeddings the set $\Delta^{+}_{\bot}$ can be empty as for the special embedding of $A_1\subset A_2$ with the embedding index equal to 4, or non-empty for example for the embedding $A_1\subset A_2\subset A_3$ which is depicted at the Figure \ref{fig:a1a2a3}.
\begin{figure}[bh]
\noindent  \centering{
  \includegraphics[width=90mm]{special_A1_A2_A3.pdf}
  \caption{Special embedding $A_1\subset A_2\subset A_3$. Grey vectors are the roots of $A_2$, thick black - of $\mathfrak{a}=A_1$, dashed black are the orthogonal roots of $A_1$ which is contained in $\mathfrak{a}_{\bot}$ }
}
  \label{fig:a1a2a3}
\end{figure}

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$. 
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

Anomalous branching coefficient $k^{(1,0)}_{1}=2$, then for anomalous branching coefficient $k^{(1,0)}_{0}$ the formula (\ref{recurrent relation}) gives us
\begin{equation}
  \label{eq:23}
  k^{(1,0)}_{0}=-1\cdot k^{(1,0)}_2 +2\cdot k^{(1,0)}_1 - 3\cdot \delta_{0,0} = 1
\end{equation}
So we have computed the branching coefficients.
\newpage
\subsubsection{Embedding of $B_2$ into $B_4$}
\label{sec:someth-high-dimens}
Consider the the regular embedding of the subalgebra $B_2$ into the algebra $B_4$.
We calculate the branching coefficients for the fundamental representation of $B_4$.
The corresponding Dynkin diagrams are in the Figure \ref{fig:dynkin}.
\begin{figure}[ph]
  \centering
  \includegraphics[width=60mm]{B4_B2_2A1.pdf}
  \caption{Dynkin diagrams}
  \label{fig:dynkin}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
\begin{figure}[h]
  \includegraphics[width=150mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

Conformal embeddings should preserve conformal invariance, so Sugawara central charge should be the same for the original and the embedded theory.
